Past Lab News

### 2025-07-03 index.qmd
add DOI
add new paper acceptance
add doi for jneurosci paper

<font color="#d08770">[May 14 2024].</font> **Paper accepted**. Sullivan SR, Lokesh R, Peters CS, Calalo J, Roth AR, Buggeln JH, Ngo TT, Carter MJ, & Cashaback JGA. (Accepted). Indecision under time pressure arises from suboptimal switching behaviour. *Journal of Neurophysiology*.

>>>>

<font color="#d08770">[June 13 2024].</font> **Paper accepted**. Calalo JA, Ngo T, Sullivan S, Roth A, Lokesh R, Buggeln JH, Strand K, Marchhart V, Carter MJ, Kurtzer I, & Cashaback JGA. (Accepted). Online movements reflect ongoing deliberation. *Journal of Neuroscience*. [https://doi.org/10.1523/JNEUROSCI.1913-24.2025](https://doi.org/10.1523/JNEUROSCI.1913-24.2025){target="_blank"}

<font color="#d08770">[May 14 2024].</font> **Paper accepted**. Sullivan SR, Lokesh R, Peters CS, Calalo J, Roth AR, Buggeln JH, Ngo TT, Carter MJ, & Cashaback JGA. (In Press). Indecision under time pressure arises from suboptimal switching behaviour. *Journal of Neurophysiology*. [https://doi.org/10.1152/jn.00563.2024](https://doi.org/10.1152/jn.00563.2024){target="_blank"}
